TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
More sec 3

We introduce specificities associated with the prediction of each object.
In particular, we present the dataset from which objects are selected and the
purpose of the selection process. Details on the similarity measure backing the
predictions is described in Section~\ref{sec:features} and two methods for
improving the quality of the predictions are presented in
Section~\ref{sec:ortho} and Section~\ref{sec:synthesis}.

\paragraph{Tactics}
To start with, we build a database of tactics consisting
of tactic-goal pairs recorded from successful tactic applications in human
proofs (see
Section~\ref{sec:recording}).
Then, during proof search, we order recorded goals according to their
similarity with a targeted goal $g$ (usually the first pending goal of a node).
The recorded pairs induce an
order on tactics. The intuition is that tactics which have been successful on
goals similar to $g$ should be tried first, since they are more likely to lead
to a proof.
This predicted tactic order is translated into a prior policy for our MCTS
algorithm (see Section~\ref{sec:policy}).
Tactic selection is also used to improve the quality of the database
of tactics during orthogonalization (see Section~\ref{sec:ortho}).

@@

\paragraph{Lists of Goals as Output of Tactics}
A dataset of tactic outputs is compiled during orthogonalization.
This set is separated into positive and negative examples (see
Section~\ref{sec:evaluation}).
List of goals that are a subset of the result of a recorded tactic on a
targeted goal are considered positive. During proof search, given a list of
goals $l$ created by a tactic, we select a set of lists of goals that are most
similar to $l$. The ratio of positive examples in the selection gives us a
prior evaluation for MCTS.

@@

\textsf{ML4PG}~\cite{DBLP:journals/corr/abs-1212-3618,DBLP:journals/mics/HerasK14}
groups related proofs using clustering
algorithms. It allows \coq users to inspire themselves from similar proofs and
notice
duplicated proofs. Comparatively, our predictions comes from a much more
detailed description of the targeted goal.\todo{and can be used as an ATP}
%However, we simply create a single label for each tactic call whereas each of
%its
%arguments is treated independently in \textsf{ML4PG}.
%Our choice is motivated by the k-NN algorithm already used in
%\holyhammer for the a of theorems.
%, which can be easly adapted to the selection of tactics but would be improved
%by a
%version that can learn to predict tactics and their arguments independently.

>>>>

We discuss below the specifics associated with the prediction of each kind of object.
In particular, we present the dataset from which objects are selected and the
purpose of the selection process. The similarity measure backing the
predictions is described in Section~\ref{sec:features} and two methods for
improving the quality of the predictions are presented in
Section~\ref{sec:ortho} and Section~\ref{sec:synthesis}.

\paragraph{Tactics}
To start with, we build a database of tactics consisting
of tactic-goal pairs recorded from successful tactic applications in human
proofs (recording will be discussed in 
Section~\ref{sec:recording}).
During proof search, the recorded goals will be reordered according to their
similarity with a target goal $g$ (usually the first pending goal of a node).
The recorded pairs induce an
order on tactics. The intuition is that tactics which have been successful on
goals similar to $g$ should be tried first, since they are more likely to lead
to a proof.
This predicted tactic order is translated into a prior policy for our MCTS
algorithm (see Section~\ref{sec:policy}).
Tactic selection is also used to improve the quality of the database
of tactics during orthogonalization (see Section~\ref{sec:ortho}).

@@

\paragraph{Lists of Goals as Output of Tactics}
A dataset of tactic outputs is compiled during orthogonalization.
This set is separated into positive and negative examples (see
Section~\ref{sec:evaluation}).
List of goals that are a subset of the result of a recorded tactic on a
target goal are considered positive. During proof search, given a list of
goals $l$ created by a tactic, we select a set of lists of goals that are most
similar to $l$. The ratio of positive examples in the selection gives us a
prior evaluation for MCTS.

@@

\textsf{ML4PG}~\cite{DBLP:journals/corr/abs-1212-3618,DBLP:journals/mics/HerasK14}
groups related proofs using clustering
algorithms. It allows \coq users to inspire themselves from similar proofs and
notice
duplicated proofs. Comparatively, our predictions comes from a much more
detailed description of the target goal.\todo{and can be used as an ATP}
%However, we simply create a single label for each tactic call whereas each of
%its
%arguments is treated independently in \textsf{ML4PG}.
%Our choice is motivated by the k-NN algorithm already used in
%\holyhammer for the a of theorems.
%, which can be easly adapted to the selection of tactics but would be improved
%by a
%version that can learn to predict tactics and their arguments independently.
